Lensing

### 2014-12-13 Papers/ms.tex
Three papers

\begin{abstract}
\end{abstract}

@@

\subsection{The hunt for dark substructures}
{\bf Review of what's been done in this area. How was it done, and what do
people believe?}

@@

>>>>

\begin{abstract}

\end{abstract}

@@

\subsection{The hunt for dark substructures}
In recent years, several galaxy-galaxy lens systems have been discovered which
are thought to contain at least one dark substructure
\citep{vegetti1, vegetti2, vegetti3}.

{\bf Review of what's been done in this area. How was it done, and what do
people believe?}

@@

\bibitem[\protect\citeauthoryear{Vegetti et 
al.}{2012}]{vegetti1} Vegetti S., Lagattuta D.~J., McKean J.~P., 
Auger M.~W., Fassnacht C.~D., Koopmans L.~V.~E., 2012, Natur, 481, 341

\bibitem[\protect\citeauthoryear{Vegetti et 
al.}{2010}]{vegetti2} Vegetti S., Koopmans L.~V.~E., Bolton A., 
Treu T., Gavazzi R., 2010, MNRAS, 408, 1969

\bibitem[\protect\citeauthoryear{Vegetti, Czoske, 
\& Koopmans}{2010}]{vegetti3} Vegetti S., Czoske O., Koopmans L.~V.~E., 2010, MNRAS, 407, 225
